Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
Removed the cut inflation

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e. $\mscenario = \AI[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets. An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
    \caption{The Cut inflation.}\label{fig:cut_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}

    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.45\linewidth}
    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}

>>>>

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e. $\mscenario = \AI[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets. An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}
